---
title: "Performance testing"
output: html_document
date: "`r Sys.Date()`"
params: 
  results: "`r data.frame()`"
---

```{r setup, include=FALSE}
# =========================================================================
# Copyright © 2019 T-Mobile USA, Inc.
# 
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
#
#    http://www.apache.org/licenses/LICENSE-2.0
#
# Unless required by applicable law or agreed to in writing, software
# distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and
# limitations under the License.
# =========================================================================

knitr::opts_chunk$set(echo = FALSE, dpi=300, error=TRUE, warning=TRUE, message=FALSE)
library(loadtest)
```

## Configuration

### Request

__URL:__ `r attr(params$results,"config")$url`

__Method:__ `r attr(results,"config")$method`

```{r show_headers, results="asis", echo=FALSE}
if(!is.null(attr(results,"config")$headers)){
  cat("__Headers:__\n\n")
  header_table <- data.frame(key = names(attr(results,"config")$headers), value = attr(results,"config")$headers, stringsAsFactors = FALSE)
  header_table$key <- paste0("`",header_table$key,"`")
  header_table$value <- paste0("`",header_table$value,"`")
  rownames(header_table) <- NULL
  print(knitr::kable(header_table))
}
```

```{r show_body, results="asis", echo=FALSE}
if(!is.null(attr(results,"config")$body)){
  cat("__Body:__\n\n")
  cat("```json\n")
  cat(jsonlite::toJSON(attr(results,"config")$body,auto_unbox=TRUE))
  cat("\n```\n\n")
}
```

### Test

* Number of threads: `r max(params$results$thread)`
* Number of loops per thread: `r nrow(params$results)/max(params$results$thread)`
* Total number of requests: `r nrow(params$results)`
* Number of failed results: `r sum(params$results$request_status == "Failure")`

```{r failed_tests, results="asis"}
if(sum(params$results$request_status == "Failure") > 0){
  cat("<div class=\"alert alert-danger\" role=\"alert\"> Warning: requests failed!</div>\n\n")
}
```
## Results

* Runtime: `r round((max(params$results$time_since_start) + results$elapsed[which.max(results$start_time)])/1000,3)` seconds
* Response speed: `r nrow(params$results)/(max(params$results$time_since_start) + results$elapsed[which.max(results$start_time)])*1000` requests per second
* Mean response time: `r mean(params$results$elapsed)` seconds

```{r plot_results, echo=FALSE}
loadtest::plot_elapsed_times(params$results)
loadtest::plot_elapsed_times_histogram(params$results)
loadtest::plot_requests_by_thread(params$results)
loadtest::plot_requests_per_second(params$results)
```
